---
title: "try"
output: html_notebook
---


```{r}
df <- read.csv('athlete_events.csv')
df[df$Year == 2016,]
```
 
1) How old were the youngest male and female participants of the 1996 Olympics?
 
```{r}
male <- min(df$Age[df$Sex == 'M' & df$Year == 1996 & is.na(df$Age) == FALSE])
female <- min(df$Age[df$Sex == 'F' & df$Year == 1996 & is.na(df$Age) == FALSE])
output <- data.frame(Yongest.male.age = male, Yongest.female.age = female, row.names = c('age'))
output
```

2) What was the percentage of male gymnasts among all the male participants of the 2000 Olympics? Round the answer to the first decimal.

```{r}
library(dplyr)
df1 <- df[!duplicated(df$Name),]
gym <- nrow(df1[df1$Sex == 'M' & df1$Year == 2000 & df1$Sport == 'Gymnastics' ,])
all <- nrow(df1[df1$Sex == 'M' & df1$Year == 2000,])
round(gym / all * 100, 1)
```

3) What are the mean and standard deviation of height for female basketball players participated in the 2000 Olympics? Round the answer to the first decimal.

```{r}
round(mean(df$Height[df$Sex == 'F' & df$Sport == 'Basketball' & df$Year == 2000]), 1)

round(sd(df$Height[df$Sex == 'F' & df$Sport == 'Basketball' & df$Year == 2000]), 1)
```

4) Find a sportsperson participated in the 2002 Olympics, with the highest weight among other participants of the same Olympics. What sport did he or she do?

```{r}
highest <- max(df1$Weight[df1$Year == 2002 & is.na(df1$Weight) == FALSE])
result <- df1[df1$Year == 2002 & df1$Weight == highest, ]
result$Sport[is.na(result$ID) == FALSE]
```

5) How many times did Pawe Abratkiewicz participate in the Olympics held in different years?

```{r}
result <- df[df$Name == 'Pawe Abratkiewicz',]
result <- result[!duplicated(result$Year),]
nrow(result)
```

6) How many silver medals in tennis did Australia win at the 2000 Olympics?

```{r}
result <- df[df$Team == 'Australia' & df$Year == 2000 & df$Medal == 'Silver' & df$Sport == 'Tennis',]
result <- result[is.na(result$ID) == FALSE,]
nrow(result)
```

7) Is it true that Switzerland won fewer medals than Serbia at the 2016 Olympics? Do not consider NaN values in Medal column.

```{r}
sdf <- df[is.na(df$Medal) == FALSE & df$Year == 2016, ]
switz <- nrow(sdf[sdf$Team == 'Switzerland',])
serb <- nrow(sdf[sdf$Team == 'Serbia',])
switz < serb
```

8) What age category did the fewest and the most participants of the 2014 Olympics belong to?

```{r}
df2 <- df[df$Year == 2014,]
df2 <- df2[!duplicated(df2$ID),]
cat1 <- nrow(df2[df2$Age >= 15 & df2$Age < 25,])
cat2 <- nrow(df2[df2$Age >= 25 & df2$Age < 35,])
cat3 <- nrow(df2[df2$Age >= 35 & df2$Age < 45,])
cat4 <- nrow(df2[df2$Age >= 35 & df2$Age <= 45,])
cat5 <- nrow(df2[df2$Age >= 45 & df2$Age <= 55,])
data.frame(from.15.to.25 = cat1, from.25.to.35 = cat2, from.35.to.45 = cat3, from.35.to.45.with.45 = cat4, from.45.to.55 = cat5)
```

9) Is it true that there were Summer Olympics held in Lake Placid? Is it true that there were Winter Olympics held in Sankt Moritz?

```{r}
nrow(df[df$Season == 'Summer' & df$City == 'Lake Placid',]) > 0
nrow(df[df$Season == 'Winter' & df$City == 'Sankt Moritz',]) > 0
```

10) What is the absolute difference between the number of unique sports at the 1995 Olympics and 2016 Olympics?

```{r}
Ol1995 <- nrow(df[df$Year == 1995 & !duplicated(df$Sport), ])
df1 <- df[df$Year == 2016,]
Ol2016 <- nrow(df1[!duplicated(df1$Sport),])
Ol2016 - Ol1995
```